\documentclass{article}
\usepackage[utf8]{inputenc}

\title{MPP Proposal}
\author{sarhertz }
\date{February 2018}

\begin{document}


How should governments collect information from their citizens? What effect does this have on privacy and freedom of speech? These are some of the questions I will explore during a Master of Public Policy. The University of Calgary's MPP program will expose me to new disciplinary frameworks, through which I will consider the economic and legal repercussions of using big data. The commodification of privacy and personal information has major implications for governments and corporations, both in terms of security and financial gains. The recent partnership between Sidewalk Labs, a division of Alphabet Inc., and Waterfront Toronto 

The recent partnership between Sidewalk Labs, a division of Google’s parent company, Alphabet Inc., and the government agency, Waterfront Toronto, 

Big data impacts every type of policy-making, from environment and energy to health. It has implications for businesses too, who use personal data for advertising.Big data will transform every type of policy-making, from environment and energy to health. 

Social credit system
Partnership between sidewalk labs and Toronto (government agency Waterfront Toronto)

 

The sheer volume and variety of information – not to mention the speed at which users generate it – will transform public and private decision-making. Large datasets can provide a level of detail and accuracy previously inaccessible to policymakers; however, since most internet data contains Personal Identifiers, using it might infringe on civil liberties. 

Big Data impacts every type of policy-making, from environment and energy to health. It has implications for businesses too, who use personal data for advertising. 

This provokes the question of whether personal advertising is an invasion of privacy, and whether or not companies are operating on surveillance-based business models. Facial recognition technologies force us to consider the relationship between privacy and private property: are our images, reputations, or personal information a form of currency for exchange? 



\maketitle

\section{Introduction}

\end{document}
